Self Regulation Ontology Retest Analyses

### 2018-04-13 code/SRO_Retest_Analyses.Rmd
refactoring

test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_03-29-2018/'

retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-29-2018/'
```

@@

@@

For most of our tasks one might wonder about improvements in performance due to learning effects.

The type of ICC we have chosen does not take within subject (between session/systematic) variance in to account. This is why Weir recommends checking whether there is a significant change based on time and examining the SEMs.

>>>>

test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_02-03-2018/'

retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-03-2018/'
```

@@

For most of our tasks one might wonder about improvements in performance due to learning effects. 
The type of ICC we have chosen does not take within subject (between session/systematic) variance in to account. This is why Weir recommends checking whether there is a significant change based on time and examining the SEMs.

@@
